---
title: "Bkm_Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rvest)
library(dplyr)
library(purrr)
library(tidyverse)
```

## 1.Data Extraction 

BKM Sektörel Gelişim reports include transaction amounts and transaction count made by credit and debit cards on sectoral basis. 
Before We start to data analyse firstly we extract data from Html and construct the suitable format that we can start analyze.

```{r extract}

extractYearMonth<- function(year,month) {
  x1<-year
  x2<-month
  url <- paste('https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=',x1,'&filter_month=',x2,'&List=Listele', sep='',collapse = NULL)
  return(url)
}

paramYear <-c('2017','2018','2019')
paramMonth <- c('01','02','03','04','05','06','07','08','09','10','11','12')
raw_data_full <- ''
    
for (i in 1:length(paramYear)) {
  for (j in 1:length(paramMonth)) {
    if (paramYear[i]=='2019' & paramMonth[j]=='07') {break}
    url<-extractYearMonth(paramYear[i],paramMonth[j])
    page <- read_html(url) #Creates an html document from URL
    df <- page%>%html_nodes("table") %>%.[(4)] %>% html_table(page, fill = TRUE,header = FALSE)  %>%  as.data.frame() %>%slice(3:max(nrow(.)))  
    df <- df %>%mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>%  mutate(yearmonth=paste(paramYear[i],paramMonth[j],sep=''))
    raw_data_full<-rbind(raw_data_full,df)
  }
}

```

### Adding Columns 

Column names and explanations are below:

  kategori :İşyeri Grubu
  kk_Islem_Adedi :İşlem Adedi(Kredi Kartı)
  bk_Islem_Adedi :İşlem Adedi(Banka Kartı)
  kk_Islem_Tutari :İşlem Tutarı(Kredi Kartı)
  bk_Islem_Tutari :İşlem Tutarı(Kredi Kartı)
  yearmonth 

```{r columnnames}

colnames(raw_data_full) <- c('kategori','kk_Islem_Adedi','bk_Islem_Adedi','kk_Islem_Tutari','bk_Islem_Tutari'                              ,'yearmonth')
head(raw_data_full,10)

```

## 2.Data Analyzing 

### 2.1.Top 3 Category with the Highest Numberf Transactions

Displaying the highest number of transactions by credit card and debit card by years.(2017 to 2019 June)
```{r analyze_1}
#Create dataset for the analyzing

raw_data <-raw_data_full
raw_data <- raw_data %>%mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>%  mutate(year=substr(yearmonth,1,4))

raw_data <-raw_data%>% group_by(kategori,year) %>% summarise(toplam_kk_adet=max(sum(as.numeric(gsub("\\.","",kk_Islem_Adedi)),na.rm=T)),toplam_bk_adet=max(sum(as.numeric(gsub("\\.","",bk_Islem_Adedi)),na.rm = T))) %>% select(year,kategori,toplam_kk_adet,toplam_bk_adet)

#Adding "toplam" column
raw_data2<-raw_data %>% mutate( toplam= (toplam_kk_adet+toplam_bk_adet))%>% select(year,kategori,toplam)%>%filter(toplam!=0)

#Filter unnecessary data
raw_data3 <-raw_data2%>%arrange(year,desc(toplam))%>%filter(kategori!='TOPLAM')

#Data set preparation for chart
by_raw_data <- raw_data3 %>% group_by(year) %>% mutate(
   rank =row_number(),vars_group = 'year'
  ) %>% filter(rank<4)

print(by_raw_data)

ggplot(by_raw_data, aes(x=year, y=toplam, fill=kategori))+
  geom_bar(stat="identity")+
#  geom_text(aes(label=toplam), vjust=1.6, color="black", size=3.5)+
  theme_minimal()+
  labs(x="Year",y="Total",title="Plot",fill="Category")+
  theme(axis.text.x = element_text(angle=30))

```

### 2.2.Monthly debit card and credit card amount.

```{r analyze_2}

KategoryDataSet <-raw_data_full  %>%group_by(yearmonth)%>% summarize(kk_Islem_Tutari= sum(as.numeric(gsub(",", ".", gsub("\\.", "", kk_Islem_Tutari))),na.rm=T),bk_Islem_Tutari= sum(as.numeric(gsub(",", ".", gsub("\\.", "", bk_Islem_Tutari))),na.rm=T))%>%mutate(year=substr(yearmonth,1,4)) %>%filter(kk_Islem_Tutari!=0)%>% select(yearmonth,kk_Islem_Tutari,bk_Islem_Tutari)



DataSet <- data.frame(YearMonth=c(KategoryDataSet$yearmonth),
  Kategory = c("Banka Kartı Tutarı","Kredi Kartı Tutarı")
  , Tutar=c(KategoryDataSet$bk_Islem_Tutari,KategoryDataSet$kk_Islem_Tutari))
DataSet
```

### 2.3.Annual Debit Card and Credit Card amount and chart.


```{r analiz3}
library(tidyverse)
library(dplyr)

KategoryDataSet_Yearly <-raw_data_full %>%mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>%  mutate(year=substr(yearmonth,1,4))%>%group_by(year)%>% summarize(kk_Islem_Tutari= sum(as.numeric(gsub(",", ".", gsub("\\.", "", kk_Islem_Tutari))),na.rm=T),bk_Islem_Tutari= sum(as.numeric(gsub(",", ".", gsub("\\.", "", bk_Islem_Tutari))),na.rm=T)) %>%filter(kk_Islem_Tutari!=0)%>% select(year,kk_Islem_Tutari,bk_Islem_Tutari)

#Chart data set
DataSet_Yearly <- data.frame(Year=c(KategoryDataSet_Yearly$year),
  Kategory = c("Banka Kartı Tutarı","Kredi Kartı Tutarı")
  , Tutar=c(KategoryDataSet_Yearly$bk_Islem_Tutari,KategoryDataSet_Yearly$kk_Islem_Tutari))

DataSet_Yearly<-DataSet_Yearly%>% arrange(Year,Kategory,Tutar)

DataSet_Yearly

ggplot(data=DataSet_Yearly, aes(x=Year, y=Tutar, group=Kategory)) +
  geom_line(aes(color=Kategory))+
  geom_point(aes(color=Kategory)) 

```